Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-07 Moltres.tex
acknowledgements

>>>>

This work was supported by the University of Illinois Department of Nuclear, 
Plasma, and Radiological Engineering, the National Center for Supercomputing 
Applications, and the University of Illinois Blue Waters Professors program. 
Undergraduate researcher Gavin Ridley was supported through NSF REU Site award 
1659702, ``INCLUSION - Incubating a New Community of Leaders Using Software, 
Inclusion, Innovation, Interdisciplinary and OpeN-Science.''

Finally, the authors would like to thank Matthew Turk and the Data Explortation 
Lab for co-supporting Dr. Lindsay during his postdoctoral appointment.
